---
title: "Landscape 생성의 101"
author: "김태경"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{(Korean) Creating a Landscape: 101}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This tutorial shows how to use the basic functions to create NK Landscape. In addition, NK Landscape can be discussed in relation to low dimensionality, modularity, asymmetric dependence, part-whole design, environmental uncertainty, occurrence of shocking events, and interrelationships between multiple different landscapes. These approaches can be modeled effectively by combining the extended functions of the rNKm package and modeling technology.

## Landscape 
```{r,eval=FALSE}

#library(devtools)
#install_github("drtagkim/rNKm")

library(rNKm) #라이브러리 읽기
fun <- landscape_gen(N=4,K=0) #landscape generation function
```
## 전체 Fitness values 구하기
To get the entire value at once, use the create_landscape() function.

```{r,eval=FALSE}
library(rNKm) #라이브러리 읽기
fun <- landscape_gen(N=4,K=0) #landscape generation function
land <- create_landscape(N=4,K=0,fun)
```

land$landscape Would look like this:

```{r,echo=FALSE,results='asis'}
library(rNKm, quietly=TRUE,warn.conflicts=FALSE) #Library reading
fun <- landscape_gen(N=4,K=0) #landscape generation function
land <- create_landscape(N=4,K=0,fun)
knitr::kable(land$landscape)
```

Landscape generation. After creating a function, you can choose individual fitness values.

```{r,eval=FALSE}
locations <- create_locations(N=4)
fun(locations[1,]) # (0,0,0,0)인 경우
fun(locations[2,]) # (1,0,0,0)인 경우
```

The binary conversion of decimal numbers is from left to right. So the binary conversion of 5 is (1,0,1,0), that is, $2^0 \times 1 + 2^1 \times 0 + 2^2 \times 1 + 2^3 \times 0 = 5$ to be.

## Influence Matrix

The Influence Matrix (IM) represents the interdependence between component elements. Even in the absence of any dependence, you must at least express your dependence (that is, the fact that you exist). For example, a 4 by 4 identity matrix.



```{r,eval=TRUE}
diag(4)
```

If the row axis means to and the column axis means from, you can think of an association relationship. This expression of dependency is familiar to those who model conceptual relationships. If it is expressed as 1 when there is a dependency relationship, for example, the influence matrix of the following 4 by 4 matrix can be constructed.



```{r, eval=TRUE}
inf_mat <- matrix(c(1,1,1,0,0,1,1,1,1,0,1,1,1,1,0,1),4)
inf_mat
```

No. 1 has a dependency relationship with elements 3 and 4, No. 2 with Nos. 1 and 4, No. 3 with Nos. 1 and 2, and No. 4 with Nos. 2 and 3. If such a dependency relationship is not defined, landscape_gen() or landscape_gen_lowdim() always assumes the latest room dependency. That is, a matrix in the form of



```{r, eval=TRUE}
inf_mat <- matrix(c(1,1,0,0,0,1,1,0,0,0,1,1,1,0,0,1),4)
inf_mat
```

## Contribution Matrix

In order to express the dependence relationship as a specific fitness value, the location information where the dependence occurs must be informed to the function. Of course, if this information is not provided to the landscape_gen() or landscape_gen_lowdim() functions, a contribution matrix that expresses the dependency relationship is constructed only with the basic form of the influence matrix. The contribution matrix can be created very simply as follows.



```{r, eval=TRUE}
inf_mat <- matrix(c(1,1,1,0,0,1,1,1,1,0,1,1,1,1,0,1),4)
contr_mat <- convert_influence_contribution(inf_mat)
contr_mat
```

Contribution matrix is transferred to PI (Part Interdependency) parameter.

```{r,eval=TRUE}
inf_mat <- matrix(c(1,1,1,0,0,1,1,1,1,0,1,1,1,1,0,1),4)
contr_mat <- convert_influence_contribution(inf_mat)
fun <- landscape_gen(N=4,K=2,PI=contr_mat)
fun(c(0,0,0,0))
fun(c(1,0,0,0))
fun(c(1,1,0,0))
```

## Landscape Plotting

When the dependence increases in the NK system, a rough landscape is otherwise created, otherwise a simple picture with global peaks is created. The simplest way to check this is to draw a 3D picture.



```{r,eval=TRUE,fig.show='hold'}
require(rNKm)
n4k0 <- create_nkm_simple(N=3,K=2) #wrapper, N=6, K=1
test_plot(n4k0)
```

Let's compare it with the following picture.

```{r,eval=TRUE,fig.show='hold'}
require(rNKm)
n4k3 <- create_nkm_simple(N=6,K=5)
test_plot(n4k3)
```
To see the results more clearly, let's run the simulation directly and find the peak points. Of course, the details will be described in more detail later, and first, execute the following code.

```{r,eval=TRUE}
require(dplyr) #data manipulation package
require(rNKm)
nk.data = create_nkm_simple(6,0) #create a landscape N=6, K=0
agent_size=10
result = search_hill_climbing_full(agent_size,nk.data$loc_ids,nk.data$nk_landscape)
do.call(rbind,lapply(result,function(x){x %>% filter(from>0 & to<0)})) #combining the final results
```

In the result, to=-1 means there is nowhere to go. Therefore, from where to = -1 is the final destination, and stabilized = TRUE describes it more clearly. Let's compare it with the following.



```{r,eval=TRUE}
require(dplyr)
require(rNKm)
nk.data = create_nkm_simple(6,5)
agent_size=10
result = search_hill_climbing_full(agent_size,nk.data$loc_ids,nk.data$nk_landscape)
do.call(rbind,lapply(result,function(x){x %>% filter(from>0 & to<0)}))
```
The case where the dependence is large (K=5) has more local peaks than the case where the dependence is small (K=0).
